Stateless Model Checking with Data-Race Preemption Points

### 2016-03-24 oopsla-16/related.tex
Expand on SATcheck and MCR.

% TODO: Expand on MCR and SATcheck.
{\bf \revision{Reduction}~techniques.} Various improvements or alternatives to DPOR have been developed, such as Dynamic Interface Reduction \cite{demeter}, Maximal Causality Reduction \cite{mcr},
%DPOR for relaxed memory models \cite{tsopso},
SAT-directed MC \cite{satcheck},
\revision{and R4 for event-driven applications \cite{r4}}.
These are all compatible with our technique.
Recent work \cite{tsopso} has extended DPOR for relaxed memory models \cite{memory-consistency-models},
which we do not yet account for in our proofs (\sect{\ref{sec:soundness}}).
Parrot \cite{parrot} combines MC with a partially-determinizing runtime for further reduction, but still, fewer than half the non-trivial \revision{tests}~in their evaluation could be completed,
\revision{which motivates \quicksand's CPU-budget-oriented approach.}
%providing a strong argument for \quicksand.

>>>>

% TODO: Expand on MCR and SATcheck.
{\bf \revision{Reduction}~techniques.} Various improvements or alternatives to DPOR have been developed, such as Dynamic Interface Reduction \cite{demeter},
%Maximal Causality Reduction \cite{mcr},
%DPOR for relaxed memory models \cite{tsopso},
%SAT-directed MC \cite{satcheck},
\revision{and R4 for event-driven applications \cite{r4}}.
These are all compatible with our technique.
%
Recent work \cite{tsopso} has extended DPOR for relaxed memory models \cite{memory-consistency-models},
which we do not yet account for in our proofs (\sect{\ref{sec:soundness}}).
%
SATCheck \cite{satcheck} and Maximal Causality Reduction \cite{mcr} replace DPOR by
%encoding the program's behaviour as a SAT or SMT formula,
%then using a solver to search for schedules guaranteed to expose new behaviour.
using a SAT or SMT solver to search for schedules guaranteed to expose new behaviour.
%These approaches provide improved
They improve
reduction by considering values read and written to identify additional independences,
while DPOR considers only addresses.
They generate new schedules at
%the granularity of each memory access,
memory access granularity,
which Iterative Deepening could allow to be relaxed for large tests in future work.
%
Parrot \cite{parrot} combines MC with a partially-determinizing runtime for further reduction, but still, fewer than half the non-trivial \revision{tests}~in their evaluation could be completed,
\revision{which motivates \quicksand's CPU-budget-oriented approach.}
